Embedding Intuitionistic into Classical Logic

### 2022-07-15 CSL/lipics-v2021-EIICL.tex
Corrections

\begin{definition}
A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$
		\item $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC}.
\todo{What does CPC stand for? Introduce abbreviation somewhere like classical predicate ... (CPC).}
\end{definition}

@@

\begin{definition}
\todo{We later also use the notion `Kripke frame', we  might introduce it here.}
\todo{Note that I have replaced `nodes' by `worlds' here.}
A \emph{Kripke structure} $\mathcal K = (W, (v_w)_{w\in W})$ consists of a partially ordered set $W$ of \emph{worlds} and a family of valuations $(v_w)_{w\in W}$ such that $v_u(A)\leq v_u(A)$ for all $u\leq w$ and propositional variables $A$ (this is called the \emph{persistency condition}).
The model relation between the $v_u$ and formulas $\varphi$ is defined as before, except in the case of implications, where we set
	\begin{itemize}
		\item $v_u\models\varphi\to \psi$ if for all $w\geq u$ we have $w\not\models\varphi$ or $u\models\psi$.
	\end{itemize}
We say that $\varphi$ is satisfied at a world $u$ if $v_u\models\varphi$ and write $u\models\varphi$. If a formula is satisfied at every world then $\mathcal K$ is a \emph{model} for $\varphi$. A formula is valid if every Kripke structure is a model of it. We denote the set of valid formulas with IPC.
\todo{introduce abbreviation}
\end{definition}
There are many classical tautologies which are not intuitionistically valid:
\begin{example}\label{LEMcounterexample}
Consider the famous law of excluded middle $A\vee\neg A$. Recall that $\neg A := A\to \bot$. As a counter-model consider a Kripke structure with two nodes $u\leq w$ and $v_u(A) = 0, v_w(A) = 1$. Then $u\not\models A$ and $u\not\models \neg A$, i.e. $u\not\models A\vee\neg A$.
\end{example}
In classical logic a proven strategy for showing that a formula valid is to consider its negation and show that it is not satisfiable. This is insufficient for intuitionistic logic, e.g. $A\vee\neg A$ is not an intuitionistic tautology but its negation is not satisfiable either.

@@

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m, &\text{if $b=a$,}\\
		v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$.
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. We denote the set of valid formulas with CQC.
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$ and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$
		\item $u, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I_u, v},\dots,t_n^{I_u, v})\in R^{I_u}$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. We denote the set of valid formulas with IQC.
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. A similar translation was proposed in~\cite{statman1979intuitionistic}.
\todo{what has been done in the previous work? just the propositional case? just classical logic? did you find a citation for the full Tseytin-like transformation somewhere? If this is new we might add it to the intro.}

@@

Then from the previous three Lemmas we get
\todo{as a general rule, I like to finish sentences with a proper grammatical ending, here `:'}

@@

We are now ready to put these two reduction together with our embedding f. Let $\varphi$ be some propositional formula. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi$$
\todo{here the previous sentence did not finish with a proper grammatical ending as well, I would add `.' after $P_\varphi$}

@@

This is as far as the first-order encoding can be simplified. What remains is the elimination of the remaining weak $\forall$-quantifiers.
\todo{delete the last two sentences?}

@@

\begin{proof}
\todo{I corrected the proof, please check again.}

@@

	2. Let $w$ be some element with $w\geq u$.
If $C^I(w)$ is true, we are done. 
Otherwise $C^I(w)$ is false.
Due to persistency $C^I(u)$ is also false.
Because $(A^I(f_\psi^I(u))\to B^I(f_\psi^I(u)))\to C^I(u)$ holds, then $A^I(f_\psi^I(u))\to B^I(f_\psi^I(u))$ must be false, i.e. $A^I(u)$ is true and $B^I(u)$ is false. Then $A^I(w)$ and $A^I(f^I_\psi(w))$ is also true due to persistency.
Because $(A^I(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I(w)$ holds, we now get that  $B^I(f^I(w))$ must be false.
But then due to persistency so is $B^I(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

Essentially what fulfilment of $\psi$ at $u$ tells us is that having $f_\psi(w) = w$ for all $w\geq u$ works.
\todo{what is meant by `having $f_\psi(w) = w$ for all $w\geq u$ works`'? Reformulate the sentence.}
With this lemma in hand showing that $(M_T, I_T)$ is a counter-model to $\varphi^\circ$ is a straightforward check of definitions.

@@

\begin{example}
	Consider
	$$\mathcal S = \{(A\to B)\to C, (B\to A)\to D, (A\wedge B)\to \bot, (C\vee D)\to E\}$$and $\varphi = \bigwedge S\to E$ which has the Kripke counter-model, depicted below,
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right)   [right=of center] {$B, C$};
			\node[squarednode]      (left)    [left=of center] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left.south east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right.south west);			
		\end{tikzpicture}
	\end{center}
	\vspace*{-.3cm}where at each node the true propositions are indicated.
%	
There is a corresponding classical counter-model $\mathcal M = (M, I)$ to $\varphi^\circ$ with $M = \{u, u_l, u_r\}$, $A^{I}(l) = D^I(l) = B^I(r) = C^I(r) = 1$ and $0$ else.
%
Denoting $\psi_1 := (A\to B)\to C$ and $\psi_2 := (A\to B)\to C$ \todo{I guess this should be $\psi_2 := (B\to A)\to D$}, this corresponds to a transformed counter-model $\mathcal M_T = (M_T, I_T)$ of $\varphi^\circ$ with $M_T = \{\epsilon, \psi_1, \psi_2, \psi_1\psi_2, \psi_2\psi_1\}$ and interpretation as presented below:
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right1)   [right=of center] {$B, C$};
			\node[squarednode]      (right2)   [above=of right1] {$B, C$};
			\node[squarednode]      (left1)    [left=of center] {$A, D$};
			\node[squarednode]      (left2)    [above=of left1] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left1.south east) node [midway, below left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right1.south west) node [midway, below right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.north) -- (left2.south) node [midway, right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.north) -- (right2.south) node [midway, left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.south west) to [out=225, in=135, loop, looseness=3] node [left] {$f_{\psi_1}$} (left1.north west);		
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.south east) to [out=315, in=45, loop, looseness=3] node [right] {$f_{\psi_2}$} (right1.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (left2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (left2.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (right2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (right2.north east);		
		\end{tikzpicture}
	\end{center}
\end{example}

@@

\begin{definition}
	Suppose $\mathcal S$ is a set of formulas $\psi$ of the form
	$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C),(A\vee B)\to C, (A\to B)\to C$$
	Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$ and $\Lambda$ the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ occurring in $\mathcal S$ and $k\in \mathcal F_\to$, consider a new atom $A^{k}$, which will correspond to $A^{I_F}(k)$ from the previous definition.
\todo{$A^{I_F}(k)$ does not exist anymore. I guess it is from a previous version?}
\todo{As a general rule, I would remove explanations from definitions, and do remarks after the definition}
Obtain $\mathcal S^\#$ by including the formulas
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $(A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occur in $k$.
	\end{itemize}
\end{definition}

\begin{theorem}
	$$\mathcal S\models_C P\text{ iff }\mathcal S^\#\models_I P^\emptyset$$
\end{theorem}

@@

\begin{lemma}
	$\varphi$ is not intuitionistically valid iff $\varphi^Q$ is a satisfiable QBF.
\end{lemma}
\begin{proof}
\todo{The proof contains some old notation at several places.}
\todo{Also the proof could be beautified a bit.}
Suppose $\varphi$ is not intuitionistically valid, i.e. there exists a counter-model $\mathcal M$ for $\mathcal S^\#\to P^\epsilon$.
For each atom $A$ interpret $A^0$ such as $\mathcal M$ interprets $A^\epsilon$. Suppose we are given interpretations of all atoms $A^i$ for $i < n$ and a sequence with no repetitions $\psi_1\dots\psi_{n-1}$ over $\mathcal F_\to$ such that $\psi_i$ is exactly the $\psi\in\mathcal F_\to$ for which $F_{\psi}^i$ is true and $A^i$ is interpreted as $A^{\psi_1\dots\psi_i}$ is in $\mathcal M$.

@@

\todo{The size analysis of the QBF reduction should be stated in some theorem in this section}

@@

However Part 2 of this Lemma does not hold for $\psi\in\mathcal F_\forall$, because even if for all $x$ with $E(x, v$) we have $A(x, v)$ there could be some term $t$ with $\neg E(t, v)$ and $w$ with $v\preceq w$ such that $E(t, w)$ and $\neg A(t, w)$. This is why we must consider sequences that have repetitions of such formulas:

@@

Even if we don't have the nice finiteness of the propositional case we have still reduced the model complexity in that we know that considering worlds of the form $$f_{\psi_1}(\vec t_1, f_{\psi_2}(\vec t_2, \dots f_{\psi_n}(\vec t_n, s)\dots))$$ is sufficient. In particular this allows us to completely eliminate $\preceq$ from the formula, that is we remove the PO-encoding \todo{PO-encoding used for the first time, say PartialOrder?}
from $K(\varphi)$ and replace $\forall u\forall w\forall x((E(x, u)\wedge u\preceq w)\to E(x, w))$ with $\bigwedge\{\forall \vec z\forall u(E(x, u)\to E(x, f_\psi(\vec z, u)))\:|\:\psi\in\mathcal F_\to\}$ and analogously for persistency to obtain $K$. Define

$$\varphi^{\#} = K\to \bigwedge S^\#\to P^\#$$
then we have
\begin{theorem}
\label{thm:fo-reduction}
	$\varphi$ is intuitionistically valid iff $\varphi^\#$ is classically valid.
\end{theorem}
The complete translation is summarised in Theorem~\ref{fullFOtranslation}.

>>>>

\begin{definition}
A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$
		\item $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC} (Classical Propositional Calculus).
\end{definition}

@@

\begin{definition}
A \emph{Kripke structure} $\mathcal K = (W, (v_w)_{w\in W})$ consists of a partially ordered set $W$ of \emph{worlds} and a family of valuations $(v_w)_{w\in W}$ such that $v_u(A)\leq v_u(A)$ for all $u\leq w$ and propositional variables $A$ (this is called the \emph{persistency condition}).
The model relation between the $v_u$ and formulas $\varphi$ is defined as before, except in the case of implications, where we set
	\begin{itemize}
		\item $v_u\models\varphi\to \psi$ if for all $w\geq u$ we have $w\not\models\varphi$ or $u\models\psi$.
	\end{itemize}
We say that $\varphi$ is satisfied at a world $u$ if $v_u\models\varphi$ and write $u\models\varphi$. If a formula is satisfied at every world then $\mathcal K$ is a \emph{model} for $\varphi$. A formula is valid if every Kripke structure is a model of it. We denote the set of valid formulas with \emph{IPC} (Intuitionistic Propositional Calculus).
\end{definition}
There are many classical tautologies which are not intuitionistically valid:
\begin{example}\label{LEMcounterexample}
Consider the famous law of excluded middle $A\vee\neg A$. Recall that $\neg A := A\to \bot$. As a counter-model consider a Kripke structure with two nodes $u\leq w$ and $v_u(A) = 0, v_w(A) = 1$. Then $u\not\models A$ and $u\not\models \neg A$, i.e. $u\not\models A\vee\neg A$.
\end{example}
In classical logic a proven strategy for showing that a formula valid is to consider its negation and show that it is not satisfiable. This is insufficient for intuitionistic logic, e.g. $A\vee\neg A$ is not an intuitionistic tautology but its negation is not satisfiable either.

@@

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m, &\text{if $b=a$,}\\
		v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$.
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. A formula is valid if every $\Sigma$-structure satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, its (Kripke) \emph{Frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$
		\item $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. A formula is valid if it is satisfied in eveery $\Sigma$-Kripke structure, it is valid for some Frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that Frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step towards obtaining a propositional formula we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. In fact our translation is often given as a first step in the Tseytin transformation after which the individual formulas are then converted to CNF, so it is well known, but we are not aware of work that uses just this step as a stand-alone. A similar translation for intuitionistic logic was also proposed in~\cite{statman1979intuitionistic}.

@@

Then from the previous three Lemmas we get:

@@

We are now ready to put these two reduction together with our embedding f. Let $\varphi$ be some propositional formula. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi.$$

@@

@@

\begin{proof}

@@

	2. Let $w$ be some element with $w\geq u$.
If $C^I(w)$ is true, we are done. 
Otherwise $C^I(w)$ is false.
Due to persistency $C^I(u)$ is also false.
Because $\psi$ is fulfilled at $u$, $A^I(u)\to B^I(u)$ must be false, i.e. $A^I(u)$ is true and $B^I(u)$ is false. Then $A^I(w)$ and $A^I(f^I_\psi(w))$ are also true due to persistency.
Because $(A^I(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I(w)$ holds, we now get that  $B^I(f^I(w))$ must be false.
But then due to persistency so is $B^I(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

Essentially what this tells us is that for every $u$ at which $\psi$ is fulfilled, in particular each $u$ in the image of $f_\psi$, we may add the assumption that $f_\psi(w) = w$ for all $w\geq u$ without changing the validity of $\psi$.
With this lemma in hand showing that $(M_T, I_T)$ is a counter-model to $\varphi^\circ$ is a straightforward check of definitions.

@@

\begin{remark}
	It is well known that Kripke Frames which are trees are complete with regard to intuitionistic logic. Our contribution is giving an explicit geometry that depends only on the structure of the considered formula.
\end{remark}

\begin{example}
	Consider
	$$\mathcal S = \{(A\to B)\to C, (B\to A)\to D, (A\wedge B)\to \bot, (C\vee D)\to E\}$$and $\varphi = \bigwedge S\to E$ which has the Kripke counter-model, depicted below,
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right)   [right=of center] {$B, C$};
			\node[squarednode]      (left)    [left=of center] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left.south east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right.south west);			
		\end{tikzpicture}
	\end{center}
	\vspace*{-.3cm}where at each node the true propositions are indicated.
%	
There is a corresponding classical counter-model $\mathcal M = (M, I)$ to $\varphi^\circ$ with $M = \{u, u_l, u_r\}$, $A^{I}(l) = D^I(l) = B^I(r) = C^I(r) = 1$ and $0$ else.
%
Denoting $\psi_1 := (A\to B)\to C$ and $\psi_2 := (A\to B)\to D$, this corresponds to a transformed counter-model $\mathcal M_T = (M_T, I_T)$ of $\varphi^\circ$ with $M_T = \{\epsilon, \psi_1, \psi_2, \psi_1\psi_2, \psi_2\psi_1\}$ and interpretation as presented below:
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right1)   [right=of center] {$B, C$};
			\node[squarednode]      (right2)   [above=of right1] {$B, C$};
			\node[squarednode]      (left1)    [left=of center] {$A, D$};
			\node[squarednode]      (left2)    [above=of left1] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left1.south east) node [midway, below left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right1.south west) node [midway, below right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.north) -- (left2.south) node [midway, right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.north) -- (right2.south) node [midway, left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.south west) to [out=225, in=135, loop, looseness=3] node [left] {$f_{\psi_1}$} (left1.north west);		
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.south east) to [out=315, in=45, loop, looseness=3] node [right] {$f_{\psi_2}$} (right1.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (left2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (left2.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (right2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (right2.north east);		
		\end{tikzpicture}
	\end{center}
\end{example}

@@

\begin{definition}
	Suppose $\mathcal S$ is a set of formulas $\psi$ of the form
	$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C),(A\vee B)\to C, (A\to B)\to C$$
	Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$ and $\Lambda$ the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ occurring in $\mathcal S$ and $k\in \mathcal F_\to$, consider a new atom $A^{k}$.
Obtain $\mathcal S^\#$ by including the formulas
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $(A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occur in $k$.
	\end{itemize}
\end{definition}

\begin{theorem}
	$\bigwedge\mathcal S\to P$ is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset$ is classically valid.
\end{theorem}

@@

\begin{lemma}
	$\varphi$ is not intuitionistically valid iff $\varphi^Q$ is a satisfiable QBF.
\end{lemma}
\begin{proof}
\todo{The proof contains some old notation at several places.}
\todo{Also the proof could be beautified a bit.}
Suppose $\varphi$ is not intuitionistically valid, i.e. there exists a classical counter-model $\mathcal M$ for $\bigwedge\mathcal S^\#\to P^\epsilon$.
For each atom $A$ interpret $A^0$ such as $\mathcal M$ interprets $A^\epsilon$. Suppose we are given interpretations of all atoms $A^i$ for $i < n$ and a sequence with no repetitions $\psi_1\dots\psi_{n-1}$ over $\mathcal F_\to$ such that $\psi_i$ is exactly the $\psi\in\mathcal F_\to$ for which $F_{\psi}^i$ is true and $A^i$ is interpreted as $A^{\psi_1\dots\psi_i}$ is in $\mathcal M$.

@@

@@

However Part 2 of this Lemma fails for $\psi\in\mathcal F_\forall$, because even if for all $x$ with $E(x, v$) we have $A(x, v)$ there could be some term $y$ with $\neg E(y, v)$ and $w$ with $v\preceq w$ such that $E(y, w)$ and $\neg A(y, w)$. This is why we must consider sequences that have repetitions:

@@

However Lemma~\ref{thm:fo-countermodel-reduction} still enables us to add some additional axioms which could help guide proof search. In particular we may assume that $f_\psi(w) = w$ if $\exists u(w = f_\psi(u))$ for $\psi\in\mathcal F_\forall$, i.e. $f_\psi$ is idempotent, and  $f_\psi(w) = w$ if $\exists u(w \geq f_\psi(u))$ for each $\psi\in\mathcal F_\to$, which is even stronger than idempotence. How adding these properties as assumption helps with proof search has to be examined. We have left them out of our translation for now for the sake of simplicity.
